\section{Syllabus}

\subsection{Covered in earlier modules}

\begin{itemize}
 \item MAS147: Functions of a real variable, complex numbers,
  differentiation, partial differentiation, vectors
 \item MAS148: Integration, ODEs, Taylor and Maclaurin series,
  L'Hôpital's Rule, equation solving, matrix algebra.
 \item MAS242: Functions of a complex variable, contour integration,
  power series, Fourier and Laplace transforms, application to
  differential equations.
\end{itemize}

\subsection{Syllabus}

\begin{itemize}
 \item Introduction and revision.
 \item Maxima and minima of functions of two variables.  Conditions
  for stationary points.  Examples.
 \item Extension to functions of three or more variables.
 \item Constraints and Lagrange multipliers.
 \item Double integrals as limits of sums.  Regions of integration.
  Types of applications, for example charge as integral of charge
  density.
 \item Integration over rectangular or circular regions.  Change of
  variables.
 \item Integration over two-dimensional regions, with change in the
  order of integration.  
 \item Introduction to three-dimensional surfaces.
 \item Spherical and cylindrical coordinate systems, and integration
  in terms of such coordinates.
 \item Volume integrals.
 \item Revision of vectors.  Scalar and vector products, derivatives,
  vector equations for lines.
 \item Scalar and vector fields.  Examples, including temperature and
  electric and magnetic fields.
 \item Gradients, directional derivatives, level surfaces and their
  normals.  Gradient identities.
 \item Divergence and curl.  Physical significance.  Identities.
 \item Iterated operators: $\nabla.(\nabla\tm u)=0$,
  $\nabla\tm\nabla f=0$, $\nabla.(\nabla f)=\nabla^2(f)$.  Closure and
  exactness.
 \item Unit vectors and differential operators in cylindrical and
  polar coordinates.
 \item Line integrals of scalars and vectors.  Path independence for
  exact vector fields.
 \item Stokes's theorem.  Orientations.  Examples and applications.
 \item Volume integrals and the divergence theorem.  Examples and
  applications.
 \item Summary and revision.
\end{itemize}

Questions:
\begin{itemize}
 \item How much have they done with partial derivatives?
 \item How happy are they with eigenvalues?
\end{itemize}


